The dictionary for characters of smooth group schemes

### 2016-05-20 followup.tex
Isomorphism changed to epimorphism, in the introduction.

In previous work \cite{cunningham-roe:13a}, we generalized the function-sheaf dictionary to
smooth commutative group schemes $G$, allowing for non-connected groups.
We gave a description of the category $\CS(G)$ of character sheaves in this context, as well
as the isomorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$.
In contrast to the connected case, $\TrFrob{G}$ may have nontrivial kernel;
we gave an explicit description of its kernel as $\Hh^2(\pi_0(\bG), \EEx)^{\Frob{}}$ \cite{cunningham-roe:13a}*{Thm. 3.6}.

@@

In order to further justify referring to objects in $\CCS(G)$ as commutative character sheaves,
suppose for the moment that $G$ is a connected, reductive algebraic group over $\Fq$.
In this case, every object in $\CCS(G)$ is a Frobenius-stable character sheaf on $G$ in the sense of \cite{lusztig:85a}*{Def.~2.10}.
Moreover, if $A$ is a character sheaf on $G$ in this sense, and if the characteristic function of $A$ is a character of $G(k)$, then the dictionary determines an object in $\CCS(G)$ from $A$.
These two rules determine an injection from $\CCSiso{G}$ to isomorphism classes of Frobenius-stable character sheaves on $G$.
Accordingly, we may refer to character sheaves on $G$ that arise in this manner as commutative character sheaves.
Of course, such sheaves represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups.

>>>>

In previous work \cite{cunningham-roe:13a}, we generalized the function-sheaf dictionary to
smooth commutative group schemes $G$, allowing for non-connected groups.
We gave a description of the category $\CS(G)$ of character sheaves in this context, as well
as an epimorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$. \todo{Changed isomorphism to epimorphism.}
In contrast to the connected case, $\TrFrob{G}$ may have nontrivial kernel;
we gave an explicit description of its kernel as $\Hh^2(\pi_0(\bG), \EEx)^{\Frob{}}$ \cite{cunningham-roe:13a}*{Thm. 3.6}.

@@

In order to further justify referring to objects in $\CCS(G)$ as commutative character sheaves,
suppose for the moment that $G$ is a connected, reductive algebraic group over $\Fq$.
In this case, every object in $\CCS(G)$ is a Frobenius-stable character sheaf on $G$ in the sense of \cite{lusztig:85a}*{Def.~2.10}.
Moreover, if $A$ is a character sheaf on $G$ in this sense, and if the characteristic function of $A$ is a character of $G(k)$, then the dictionary determines an object in $\CCS(G)$ from $A$.
These two rules determine an injection from $\CCSiso{G}$ to isomorphism classes of Frobenius-stable character sheaves on $G$.
Accordingly, we may refer to character sheaves on $G$ that arise in this manner as commutative character sheaves.
Of course, such sheaves represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields.
